### 2015-04-20 analysis/e5_analysis.Rmd
e5 analysis

Exclude non-compliant participants and non-English speakers.

```{r}
compliant <- d.raw %>% 
  filter(grepl("training", scale)) %>%
  group_by(workerid) %>%
  summarise(compliant = judgment[scale == "training1"] == 5 & 
              judgment[scale == "training2"] == 1)

d <- d.raw %>% 
  left_join(compliant) %>%
  filter(grepl(pattern = "english", 
               language, ignore.case = TRUE), 
         domain != "training1", 
         domain != "training2", 
         compliant == TRUE)
```

@@

```{r}
ms <- d %>%
  group_by(knowledge) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment))

pdf("plots/e4.pdf",width=4)
qplot(x = knowledge, y = judgment, fill=knowledge, 
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih),
                 position = position_dodge(width=.9)) + 
  ylab("Does the inference follow? 1=yes, 0=no")
dev.off()
```

Next break down by domain condition.

```{r}
ms <- d %>%
  group_by(domain, knowledge) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment), 
            n = n())

# pdf("plots/e3_level.pdf")
qplot(x = domain, y = judgment, 
      fill = knowledge,
      geom = "bar", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih),
                 position = position_dodge(width=.9)) + 
  ylab("Does the inference follow? 1=yes, 0=no")
# dev.off()
```

Statistics

```{r}

summary(glmer(judgment ~ knowledge + (1 | workerid) + 
                (knowledge | domain), 
              data = d,
              family = "binomial"))

summary(glmer(judgment ~ knowledge + (1 | workerid) + 
                (1 | domain), 
              data = d,
              family = "binomial"))

```

>>>>

Holding off on exclusions - everyone put English, and training 2 was confusing.

```{r}
# compliant <- d.raw %>% 
#   filter(grepl("training", scale)) %>%
#   group_by(workerid) %>%
#   summarise(compliant = judgment[scale == "training1" & degree == "hi"] > 3 & 
#               judgment[scale == "training1" & degree == "low"] < 3)
#   
# d <- d.raw %>% 
#   left_join(compliant) %>%
#   filter(grepl(pattern = "english", 
#                language, ignore.case = TRUE), 
#          domain != "training1", 
#          domain != "training2", 
#          compliant == TRUE)
d <- d.raw %>% filter(scale != "training1")
```

@@

```{r}
ms <- d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            judgment = mean(judgment))

qplot(x = stars, y = judgment, col = degree,
      geom = "line", stat = "identity", 
      position = "dodge", 
      data = ms) + 
  geom_linerange(aes(ymin = judgment - cil, 
                     ymax = judgment + cih)) + 
  facet_wrap(~scale)
```
